Import and Tidy ADFG Supplied Location and Haul-out Data

### 2021-06-08 data_raw/adfg/adfg_tidydata.Rmd
FINALIZING ADFG DATA PROCESSING

adfg_timelines <- readr::read_csv('ADFG_SealTimelineData3.csv',
                                  col_types = adfg_timeline_cols) %>% 
  dplyr::mutate(GMTDate = as.Date(GMTDate, origin = "1899-12-30", 
                                     tz = "UTC") %>% 
                  lubridate::as_datetime(),
                Ptt = as.integer(Ptt),
                TagType = toupper(TagType)) %>% 
  dplyr::rename(deployid = DeployIDs,
                tag_type = TagType,
                hist_type = HistType,
                date_time = GMTDate) %>% 
  dplyr::rename_all(tolower) %>% 
  dplyr::select(-c(monthnumb,latitude,longitude,locationquality,sum,hist_type))

@@

adfg_timelines <- adfg_timelines %>% 
        tidyr::gather(bin, percent_dry, starts_with('bin')) %>%
        dplyr::left_join(bins, by = "bin") %>%
        dplyr::mutate(date_time = date_time + lubridate::hours(hour),
                      data_date = lubridate::floor_date(date_time,"day")) %>%
        dplyr::select(c(deployid,ptt,tag_type,date_time,data_date,percent_dry)) %>% 
        dplyr::arrange(deployid,date_time)
```

>>>>

adfg_timelines <- readr::read_csv('ADFG_SealTimelineData3.csv',
                                  col_types = adfg_timeline_cols) %>% 
  dplyr::mutate(GMTDate = as.Date(GMTDate, origin = "1899-12-30", 
                                     tz = "UTC") %>% 
                  lubridate::as_datetime(),
                Ptt = as.integer(Ptt),
                TagType = toupper(TagType)) %>% 
  dplyr::rename(speno = DeployIDs,
                tag_type = TagType,
                hist_type = HistType,
                date_time = GMTDate) %>% 
  dplyr::rename_all(tolower) %>% 
  dplyr::mutate(deployid = paste(speno,tag_type, sep = "_")) %>% 
  dplyr::relocate(deployid) %>% 
  dplyr::select(-c(monthnumb,latitude,longitude,locationquality,sum,hist_type))

@@

adfg_timelines <- adfg_timelines %>% 
        tidyr::gather(bin, percent_dry, starts_with('bin')) %>%
        dplyr::left_join(bins, by = "bin") %>%
        dplyr::mutate(date_time = date_time + lubridate::hours(hour),
                      data_date = lubridate::floor_date(date_time,"day")) %>%
        dplyr::select(c(deployid,speno,ptt,tag_type,date_time,data_date,percent_dry)) %>% 
        dplyr::arrange(deployid,date_time)
```
